### 2020-11-18 CV/cv-sections/education.tex
CV small update

\cventry
{BSc in Applied Mathematics and Physics} % Degree
{Moscow Institute of Physics and Technology} % Institution
{Moscow, Russia} % Location
{Sep. 2014 - Jun. 2018} % Date(s)
{ % Description(s) bullet points
}

>>>>

\cventry
{BS in Applied Mathematics and Physics} % Degree
{Moscow Institute of Physics and Technology} % Institution
{Moscow, Russia} % Location
{Sep. 2014 - Jun. 2018} % Date(s)
{ % Description(s) bullet points
}
